Interactive Markdown to explore Clustering

### 2017-06-14 src/ClusterComparison.Rmd
bugfix in compClustering and minor changes

clustDat <- filter(clustDat, Statistic=="Average Silhouette Width")
compPlot <- ggplot(clustDat, aes(x=as.character(DeepSplit), y=Value, color=Linkage,
			    group=Linkage)) +
geom_point() +
geom_path() +
facet_grid(.~Dissimilarity, scales="free_y")
compPlot

@@

#Compare Cluster stability 
# boot1 <- bootDat[["euclidean_average_0"]]

#Clustering
# clust1 <- dynamicCluster(m.sub, dm="euclidean",
#                          lk="average",
#                          ds=0,
#                          output="Cluster")
# clust2 <- dynamicCluster(m.sub, dm="pearson",
#                          lk="average",
#                          ds=0,
#                          output="Cluster")
# clust3 <- dynamicCluster(m.sub, dm="pearson",
#                          lk="ward.D2",
#                          ds=0,
#                          output="Cluster")

#Looking a different clusters in depth
# 
# fPCA <- t(trafM)
# fPCA <- scale(fPCA,scale=TRUE,center=TRUE)
# set.seed(rnd_seed)
# tsn <- Rtsne(fPCA,perplexity=10,initial_dims=5)
# pD$tSNE1 <- tsn$Y[,1]
# pD$tSNE2 <- tsn$Y[,2]
# tsnePlot <- ggplot(pD, aes(x=tSNE1, y=tSNE2, shape=Condition, color=as.factor(cluster))) +
#     geom_point(alpha=0.8,size=2) +
#     theme_bw()
# tsnePlot
# 
# tsnePlot <- ggplot(pD.filtered, aes(x=tSNE1, y=tSNE2, color=log2(Acta2+1), shape=Replicate)) +
#     geom_point(alpha=0.8,size=2) +
#     theme_bw()
# tsnePlot
```

>>>>

clustDat <- filter(clustDat, Statistic=="Average Silhouette Width")
compPlot <- ggplot(clustDat, aes(x=as.character(DeepSplit), y=Value, color=Linkage,
			    group=Linkage)) +
geom_path() +
geom_point(aes(size=K)) +
facet_grid(.~Dissimilarity, scales="free_y") +
ylab("Average Silhouette Width") +
compPlot

@@

```
